### 2017-09-29 TF-vldb2018/sec-appendix.tex

\noindent
{\textbf{1. Proof of Theorem~\ref{thm-tsim-radius}}}

@@

\noindent
{\textbf{2. Proof of Proposition~\ref{thm-inc-grouprec-pat}}}

@@

\noindent
{\textbf{3. Proof of Theorem~\ref{thm-compose}}}

@@

\noindent
{\textbf{4. Proof of Proposition~\ref{prop-fragmentation}}}

@@

\noindent
{\textbf{5. Proof of Proposition~\ref{prop-canaffballs}}}

@@

\noindent
{\textbf{6. Proof of Proposition~\ref{prop-affected-datainc}}}

>>>>

\noindent
{\textbf{1. Proof of Proposition~\ref{prop-pattern-consistency}}}

The satisfiability of patterns $P$ can be checked by treating $P$ as both data and pattern graphs, and computing the maximum match relation $M$ in $P$ for $P$, via graph simulation.
Indeed, pattern $P$ is satisfiable iff for each $(u, v)\in M$ with the capacity bounds $[x_u, y_u]$ on $u$ and $[x_v, y_v]$ on $v$, respectively, $x_v \leq y_u$ holds. 
Observe that computing graph simulation and the size of $M$ is bounded by $|P|^2$.

\noindent
{\textbf{2. Proof of Theorem~\ref{thm-tsim-radius}}}

@@

\noindent
{\textbf{3. Proof of Proposition~\ref{thm-inc-grouprec-pat}}}

@@

\noindent
{\textbf{4. Proof of Theorem~\ref{thm-compose}}}

@@

\noindent
{\textbf{5. Proof of Proposition~\ref{prop-fragmentation}}}

@@

\noindent
{\textbf{6. Proof of Proposition~\ref{prop-canaffballs}}}

@@

\noindent
{\textbf{7. Proof of Proposition~\ref{prop-affected-datainc}}}
